\phantomsection\addcontentsline{toc}{section}{Références / Webographie}

\renewcommand{\refname}{Webographie}
\newcounter{firstbib}

\begin{thebibliography}{ABC}

    \bibitem{cartopendata} LiberTIC. \emph{OpenData Map}. URL: \url{http://www.opendata-map.org/}. Consulté le 1 juin 2015.

    \bibitem{gitimmersion} Gitimmersion. \emph{Best GIT tuto ever -50 steps}. URL: \url{http://gitimmersion.com/}. Consulté le 13 avril 2015.

    \bibitem{successfulgit} Vincent Driessen. \emph{A successful Git branching model}. Janvier 2010. URL: \url{http://nvie.com/posts/a-successful-git-branching-model/}. Consulté le 13 avril 2015.

    \bibitem{bestpracticephp} Brian Fenton. \emph{Best Practices for Modern PHP Development}. URL: \url{https://www.airpair.com/php/posts/best-practices-for-modern-php-development}. Consulté le 14 avril 2015.

    \bibitem{stupidvssolid} Hugo Hamon. \emph{Votre code est STUPID ? Rendez le SOLID}. Décembre 2013. URL: \url{http://afsy.fr/avent/2013/02-principes-stupid-solid-poo}. Consulté le 14 avril 2015.

    \bibitem{symfonybook} Sensio Labs. \emph{The Symfony Book}. URL: \url{http://symfony.com/doc/current/book/index.html}. Consulté de nombreuses fois du 15 avril 2015 au 19 juin 2015.

    \bibitem{restsymfony} William Durand. \emph{REST APIs with Symfony2: The Right Way}. Août 2012. URL: \url{http://williamdurand.fr/2012/08/02/rest-apis-with-symfony2-the-right-way/}. Consulté le 22 mai 2015.

    \bibitem{hateoas} The RESTful CookBook. \emph{What is HATEOAS and why is it important for my REST API?}. URL: \url{http://restcookbook.com/Basics/hateoas/}. Consulté le 12 juin 2015.

    \bibitem{restandhateoas} XEmacs Slartibarfast. \emph{Representational State Transfer (REST) and HATEOAS}. Novembre 2013. URL: \url{http://fr.slideshare.net/XEmacs/representational-state-transfer-rest-and-hateoas}. Consulté le 12 juin 2015.

    \bibitem{richardson} Leonard Richardson. \emph{Act Three: The Maturity Heuristic}. Octobre 2008. URL: \url{http://www.crummy.com/writing/speaking/2008-QCon/act3.html}. Consulté le 12 juin 2015.

    \setcounter{firstbib}{\value{enumiv}}
\end{thebibliography}

\renewcommand{\refname}{RFCs}

\begin{thebibliography}{ABC}
    \setcounter{enumiv}{\value{firstbib}}

    \bibitem{rfc4918} RFC 4918. \emph{HTTP Extensions for Web Distributed Authoring and Versioning}. URL: \url{https://tools.ietf.org/html/rfc4918}.

    \bibitem{rfc4791} RFC 4791. \emph{Calendaring Extensions to WebDAV}. URL: \url{https://tools.ietf.org/html/rfc4791}.

    \bibitem{rfc6352} RFC 6352. \emph{vCard Extensions to WebDAV}. URL: \url{https://tools.ietf.org/html/rfc6352}.

    \bibitem{rfc5545} RFC 5545. \emph{Internet Calendaring and Scheduling Core Object Specification}. URL: \url{https://tools.ietf.org/html/rfc5545}

    \bibitem{rfc6350} RFC 6350. \emph{vCard Format Specification}. URL: \url{https://tools.ietf.org/html/rfc6350}.

    \bibitem{rfc7265} RFC 7265. \emph{jCal: The JSON Format for iCalendar}. URL: \url{https://tools.ietf.org/html/rfc7265}.

\end{thebibliography}
